	
	
	\begin{abstract}
		This document formalizes and develops the mathematics for several hypotheses concerning the Bekenstein Bound and the quantum and classical information content of a system, particularly in the context of black holes.
	\end{abstract}
	
	\section{Definitions and Notation}
	
	Let $\mathcal{S}$ be a physical system contained within a spatial region with surface area $A$. We define the following quantities:
	\begin{itemize}
		\item $l_P = \sqrt{\frac{\hbar G}{c^3}}$: Planck length.
		\item $A$: Surface area of the region containing the system $\mathcal{S}$.
		\item $I_B(\mathcal{S})$: Bekenstein Bound for the system $\mathcal{S}$, representing the maximum information that can be contained within the region of area $A$, given by $I_B(\mathcal{S}) = \frac{A}{4 l_P^2 \ln 2}$.
		\item $\rho_{\mathcal{S}}$: The quantum state (density matrix) of the system $\mathcal{S}$.
		\item $S(\rho_{\mathcal{S}}) = -\text{Tr}(\rho_{\mathcal{S}} \ln \rho_{\mathcal{S}})$: The von Neumann entropy of the system $\mathcal{S}$ (in nats).
		\item $I_Q(\mathcal{S}) = \frac{S(\rho_{\mathcal{S}})}{\ln 2}$: The total quantum information of the system $\mathcal{S}$ (in bits).
		\item $I_C(\mathcal{S})$: The maximum classically accessible information of the system $\mathcal{S}$ (in bits). This depends on the specific measurements performed and the subsystem being observed. For a system $\mathcal{S}$ and an observer making classical measurements on a subsystem $\mathcal{A} \subset \mathcal{S}$, $I_C(\mathcal{S})$ is related to the Shannon entropy obtained from the probabilities of measurement outcomes, maximized over all possible classical measurements on $\mathcal{A}$. If the measurement is optimal and reveals all classical correlations within $\mathcal{A}$, then $I_C(\mathcal{S})$ can be related to the von Neumann entropy of the reduced density matrix of $\mathcal{A}$, $S(\rho_{\mathcal{A}}) = -\text{Tr}(\rho_{\mathcal{A}} \ln \rho_{\mathcal{A}})$, such that $I_C(\mathcal{S}) \approx \frac{S(\rho_{\mathcal{A}})}{\ln 2}$. The precise definition of $I_C(\mathcal{S})$ will depend on the context of the system and the observer.
	\end{itemize}
	
	\section{Hypotheses Formalization}
	
	We now formalize the given hypotheses using the definitions above.
	
	\subsection{Null Hypothesis (H0)}
	
	The Bekenstein Bound is greater than or equal to the total quantum information of the system $\mathcal{S}$:
	
	\begin{equation*}
		H_0: I_B(\mathcal{S}) \ge I_Q(\mathcal{S})
	\end{equation*}
	
	Substituting the definitions:
	
	\begin{equation*}
		H_0: \frac{A}{4 l_P^2 \ln 2} \ge \frac{S(\rho_{\mathcal{S}})}{\ln 2}
	\end{equation*}
	
	\begin{equation*}
		H_0: S(\rho_{\mathcal{S}}) \le \frac{A}{4 l_P^2}
	\end{equation*}
	
	This is the standard formulation of the Bekenstein Bound in terms of von Neumann entropy.
	
	\subsection{Alternative Hypothesis 1 (H1)}
	
	The Bekenstein bound is greater than or equal to the maximum classically accessible information of the system $\mathcal{S}$:
	
	\begin{equation*}
		H_1: I_B(\mathcal{S}) \ge I_C(\mathcal{S})
	\end{equation*}
	
	Substituting the definition of $I_B$:
	
	\begin{equation*}
		H_1: \frac{A}{4 l_P^2 \ln 2} \ge I_C(\mathcal{S})
	\end{equation*}
	
	If we consider a classical observer measuring a subsystem $\mathcal{A}$ with reduced density matrix $\rho_{\mathcal{A}}$, and the maximum classically accessible information is related to its von Neumann entropy, then:
	
	\begin{equation*}
		H_1: \frac{A}{4 l_P^2 \ln 2} \ge \frac{S(\rho_{\mathcal{A}})}{\ln 2} \implies S(\rho_{\mathcal{A}}) \le \frac{A}{4 l_P^2}
	\end{equation*}
	
	The subsystem $\mathcal{A}$ being measured must be contained within the region of area $A$.
	
	\subsection{Alternative Hypothesis 2 (H2) for Black Holes}
	
	For a black hole $\mathcal{B}$, the total quantum information is equal to the maximum classically accessible information:
	
	\begin{equation*}
		H_2: I_Q(\mathcal{B}) = I_C(\mathcal{B})
	\end{equation*}
	
	This hypothesis suggests that for black holes, all the quantum information can, in principle, be retrieved through classical measurements on the emitted radiation or the final state of the black hole. If we consider the black hole system to include the black hole itself and its Hawking radiation, and the classical information is obtained from measurements on the radiation, this hypothesis relates the total quantum entropy of the combined system to the classical information gained by an observer.
	
	\section{Meta-hypothesis: Black Hole Evolution}
	
	The meta-hypothesis posits that black holes at different stages of existence and dissolution exhibit all three properties. Let $\mathcal{B}(t)$ represent a black hole at time $t$ during its evolution.
	
	\begin{enumerate}
		\item \textbf{Bekenstein Bound and Total Quantum Information:} There exists a time interval during the black hole's existence such that $I_B(\mathcal{B}(t)) \ge I_Q(\mathcal{B}(t))$. This is expected to hold throughout the black hole's lifetime, as the Bekenstein Bound is believed to be a fundamental limit on the information content of any system within a given region.
		
		\item \textbf{Bekenstein Bound and Classically Accessible Information:} There exists a time interval during the black hole's existence such that $I_B(\mathcal{B}(t)) \ge I_C(\mathcal{B}(t))$. This should also hold, as the classically accessible information is a subset of the total information content and thus should also be bounded by the Bekenstein Bound.
		
		\item \textbf{Equality of Quantum and Classical Information for Black Holes:} There exists a stage in the black hole's existence (possibly at the end of its evaporation, or considering the entire process) where $I_Q(\mathcal{B}) = I_C(\mathcal{B})$. This is related to the resolution of the black hole information paradox, suggesting that all information about the black hole's formation and evolution is encoded in the outgoing radiation in a way that can be, in principle, classically accessed.
		
		\item \textbf{Observer Inaccessibility:} The meta-hypothesis further suggests that as long as the black hole has not totally evaporated, there will be information about it that is not classically accessible due to observer dependence and the nature of black holes.
		
		Let an observer $\mathcal{O}_1$ attempt to make optimal classical measurements to access information about a black hole $\mathcal{B}$. The process of making these measurements might involve interactions that alter the system or require the observer to be in a specific spacetime region.
		
		Consider an observer $\mathcal{O}_2$ who is far away from the black hole and attempts to gather information from the Hawking radiation. The information accessible to $\mathcal{O}_2$ at a given time might not be the complete quantum information of the black hole at that time.
		
		The statement about optimal classical measurements leading to the observer becoming classically inaccessible to others and consumed by the black hole can be related to scenarios where an observer attempting to gain information by falling into the black hole loses the ability to communicate with observers outside.
		
		Let $I_{Q, BH}(t)$ be the quantum information of the black hole at time $t$, and $I_{Q, rad}(t)$ be the quantum information of the radiation emitted up to time $t$. The total quantum information of the system (black hole + radiation) is conserved (assuming unitary evolution).
		
		Let $I_{C, rad}(t)$ be the classically accessible information obtained by an outside observer from the radiation up to time $t$.
		
		The meta-hypothesis suggests that for $t < t_{evaporation}$ (where $t_{evaporation}$ is the time of complete evaporation):
		
		\begin{itemize}
			\item $I_B(\mathcal{B}(t)) \ge I_Q(\mathcal{B}(t))$
			\item $I_B(\mathcal{B}(t)) \ge I_{C, rad}(t)$
			\item Possibly, $\lim_{t \to t_{evaporation}} I_Q(\mathcal{B}(t) + radiation(t)) = \lim_{t \to t_{evaporation}} I_{C, rad}(t)$
			\item There exists some $I_{private}$ about the black hole (e.g., information about its interior state) such that $I_{private} \subseteq I_Q(\mathcal{B}(t))$ and $I_{private}$ is not accessible to observers outside the event horizon through classical measurements on the radiation at that time.
		\end{itemize}
		
		The formal mathematical development of the meta-hypothesis regarding observer inaccessibility requires a more detailed framework involving quantum information theory in curved spacetime and the precise definition of "classically accessible" in such contexts. This could involve concepts like quantum entanglement between the black hole and the radiation, and the limitations imposed by the event horizon on information retrieval.
		
		One way to think about this is through the lens of complementarity. An observer falling into the black hole might access information that is not available to an outside observer, and vice versa. The descriptions of reality for these two observers might be complementary but not simultaneously accessible to a single classical observer.
		
		The statement about optimal classical measurements leading to the observer being consumed relates to the idea that to gain detailed classical information about the black hole near its horizon, an observer might need to interact with it strongly, potentially crossing the horizon and becoming part of the black hole system, thus losing the ability to communicate the information classically to the outside.
		
		This aspect of the meta-hypothesis touches upon the fundamental challenges in reconciling quantum mechanics and general relativity, particularly concerning the nature of observation and information in strong gravitational fields. A full mathematical formalization would likely require a theory of quantum gravity.
		
	\end{enumerate}
	
